Modelling BCG vaccination in the UK

### 2019-06-19 rmds/08-model-development.Rmd
review model-dev

\begin{equation}
  \alpha^T_a = 1 - e^{\mathcal{N}(log(RR), SE)}
  (\#eq:rr-to-alpha)
\end{equation}

@@

```{r summary-scenarios}
kable(scenarios_table, caption = "Summary of planned scenario analyses to be carried out in the next chapter as part of model fitting by comparision of the goodness of fit to the data.", booktabs = TRUE, escape = FALSE) %>% 
  column_spec(c(1), width = "2cm") %>% 
  column_spec(c(2), width = "8cm")
```

>>>>

\begin{equation}
  \alpha^T_a = 1 - e^{\mathcal{N}(\text{ln}(RR), SE)}
  (\#eq:rr-to-alpha)
\end{equation}

@@

```{r summary-scenarios}
kable(scenarios_table, caption = "Summary of planned scenario analyses to be carried out in the next chapter as part of model fitting by comparision of the goodness of fit to the data.", booktabs = TRUE, escape = FALSE) %>% 
  column_spec(c(1), width = "4cm") %>% 
  column_spec(c(2), width = "8cm")
```
